---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Theoretical Discription  
    This package is another version of two graph problems, MST(minimun spanning tree) and SSSP(single-source shortest-path)  
  * For MST, uses the Kruskal algoritm  
  * For SSSP, uses Dijkstra algorithm for undirected graph, and Bellman-Ford algorithm for directed graph   
  
  
### Usage
    This package includes two functions, mstree and sssp  
    For mstree, there is only one parameter `g` which is the graph used to generate MST. The output is the MST of g, in the form of a subgraph of g.  
    For sssp, there are three parameters `g` `startpoint` and `endpoint`, representing the graph, start of the path and end of the path. The output is the set of vertices on the shortest path.  
    
### Import Package
```{r setup}
library(mygraph)
```

### Run Function on small sample
```{r}
library(igraph)
m=matrix(c(0,1,5,0,2,4,0,3,3,1,5,3,1,4,5,2,5,3,2,6,2,6,3,2,4,1,5,4,7,4,5,7,3,6,7,5)+1,ncol=3,byrow=T)
g=make_graph(t(m[,1:2]),directed=TRUE)
graph_attr(g,"weight")=m[,3]
#plot(g,edge.label=graph_attr(g,"weight"))
sssp(g,1,7)
mstree(g)
```

### Compare with outcomes of package "igraph"
```{r}
st=shortest_paths(g,from=1,to=7,weights=graph_attr(g,"weight"))
!(FALSE %in% (sssp(g,1,7)==st$vpath[[1]]))

tree=mst(g,weights=graph_attr(g,"weight"))
m1=get.edgelist(mstree(g)); m1=matrix(as.numeric(m1),ncol=2)
m1=m1[order(m1[,2]),]; m1=m1[order(m1[,1]),]
m2=get.edgelist(tree); m2=m2[order(m2[,2]),]; m2=m2[order(m2[,1]),]
!(FALSE %in% (m1==m2))
```

### Compare correctness and efficiency of the package and igraph package
This package is a bit slower than igraph packages, but not much
```{r}
nvert=100   #number of vertices
nedge=500  #number of edges
m=matrix(0,nrow=nedge,ncol=3)
set.seed(1234)
m[,1]=as.integer(runif(nedge,min=1,max=nvert+0.99))
m[,2]=as.integer(runif(nedge,min=1,max=nvert+0.99))
m[,3]=abs(rnorm(nedge))+1
nvert=max(m[,1:2])

#testing in directed graph
g1=make_graph(t(m[,1:2]),directed=TRUE)
graph_attr(g1,"weight")=m[,3]
!(FALSE %in% (sssp(g1,1,nvert)==shortest_paths(g1,from=1,to=nvert,weights=graph_attr(g1,"weight"))$vpath[[1]]))
system.time(sssp(g1,1,nvert))
system.time(shortest_paths(g1,from=1,to=nvert,weights=graph_attr(g1,"weight")))

#testing in undirected graph
g2=make_graph(t(m[,1:2]),directed=FALSE)
graph_attr(g2,"weight")=m[,3]
!(FALSE %in% (sssp(g2,1,nvert)==shortest_paths(g2,from=1,to=nvert,weights=graph_attr(g1,"weight"))$vpath[[1]]))
system.time(sssp(g2,1,nvert))
system.time(shortest_paths(g2,from=1,to=nvert,weights=graph_attr(g2,"weight")))

#testing MST
tree=mst(g1,weights=graph_attr(g1,"weight"))
m1=get.edgelist(mstree(g1)); m1=matrix(as.numeric(m1),ncol=2)
m1=m1[order(m1[,2]),]; m1=m1[order(m1[,1]),]
m2=get.edgelist(tree); m2=m2[order(m2[,2]),]; m2=m2[order(m2[,1]),]
!(FALSE %in% (m1==m2))
system.time(mstree(g1))
system.time(mst(g1,weights=graph_attr(g1,"weight")))
```
